\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\begin{center}
\Large\textbf{Development of a Hybrid Robotic Surface Finishing Framework Based on Geometric Planning, Reinforcement Learning, Force-Aware Imitation Learning, and Feature Masking}
\end{center}

This thesis draft proposes a hybrid robotic surface-finishing framework for processing an entire product rather than a single isolated surface region. The proposed framework separates the problem into four interacting modules. First, a tool-footprint-aware geometric planner generates a full-coverage path over a CAD or reconstructed surface while accounting for the effective polishing-tool width, overlap, surface boundary, tool orientation, and manipulator feasibility. Second, a reinforcement-learning policy modulates the sliding velocity along the reference path to reduce spatial variation of the pressure--velocity product and the resulting material removal. Third, a force-aware imitation-learning policy generates local pose--force action chunks for edges, narrow transitions, and hardware-adjacent regions that are difficult to represent through a single geometric rule set. Fourth, a feature-masking module uses object-centric region representations inspired by VIOLA and predictive future-mask plans inspired by Mask2Act to reduce reliance on reflections and background distractors.

All high-level trajectory generators share a common 9-D waypoint representation consisting of Cartesian position, orientation, and desired force. A deterministic low-level admittance controller executes the generated trajectory and compensates for measured force error. The proposed reinforcement-learning policy does not directly command robot joints or change the geometric path; it produces only a bounded path-progress or velocity scale. Similarly, imitation learning is applied selectively to short difficult segments instead of the complete product surface, thereby reducing demonstration cost and preserving the interpretability of global coverage planning.

A guitar is selected as the primary demonstration object because a single instrument contains broad coated surfaces, strongly curved boundaries, cutaways, neck transitions, frets, pickup covers, bridges, and other small reflective metal components. The body provides a suitable test of CAD-based full coverage, whereas local components expose the perception and contact challenges targeted by force-aware imitation learning and feature masking. Planned experiments compare geometry-only planning, advanced contact-point planning, manual local programming, vision-only imitation learning, force-observation imitation learning, direct pose--force imitation learning, fixed speed, inverse-Preston control, model-based speed control, and reinforcement-learning-based velocity modulation. The main metrics are coverage ratio, uncovered boundary area, removal-rate and measured-removal variation, force tracking, contact loss, collision and intervention rates, programming and teaching time, and generalization to unseen geometry, appearance, wear, friction, and pad conditions.

\vspace{0.5cm}
\noindent\textbf{Keywords:} Robotic Surface Finishing, Full-Coverage Path Planning, Tool Footprint, Reinforcement Learning, Force-Aware Imitation Learning, Feature Masking, VIOLA, Mask2Act, Admittance Control
