\chapter{Related Work}
\label{chap:related_work}

\section{Robotic Polishing and Surface Finishing}
Robotic surface finishing combines surface representation, path generation, process planning, and contact control. Coverage planners reason about workpiece boundaries, tool footprints, local surface normals, reachability, and collision constraints~\cite{schneyer2023segmentation,mcgovern2024coverage,tafuro2024autonomous}. Force-controlled polishing methods complement geometric planning by regulating contact on curved surfaces~\cite{mohsin2019path,min2024force}. Integrated systems such as RoboGrind demonstrate that inspection, task specification, trajectory generation, and force-controlled execution can form a practical surface-treatment workflow~\cite{alt2024robogrind}.

These methods establish the importance of both geometry and contact. FAIRE addresses a different question: how to reproduce a task-specific motion--force demonstration and then correct its execution reactively. It does not claim that learning eliminates geometric or process knowledge, nor that a demonstrated trajectory guarantees full-surface coverage. Its evaluation is centered on force tracking, contact stability, normal alignment, and surface-quality consistency for specified polishing regions.

\section{Imitation Learning for Contact-Rich Manipulation}
Modern visuomotor imitation policies can generate temporally coherent action sequences from image and robot-state observations~\cite{zhao2023act,chi2025diffusionpolicy}. Contact-rich tasks expose an observation gap because the image and pose may not reveal the force transmitted through the environment. A survey of contact-rich imitation learning describes force, tactile, and compliance information as central to closing this gap~\cite{tsuji2025contactsurvey}.

Force-aware methods use interaction measurements in different ways. Admittance Visuomotor Policy Learning predicts a desired force and executes it through an admittance mechanism for general contact-rich manipulation~\cite{zhou2024admitdiff}. ForceMimic combines force--motion demonstration capture with learned pose and wrench parameters and hybrid force--position execution~\cite{liu2025forcemimic}. FoAR conditions a high-frequency reactive position policy on force/torque observations rather than using a predicted desired force trajectory as the policy action~\cite{he2025foar}. MOMA-Force similarly demonstrates visual--force imitation in mobile manipulation~\cite{yang2023momaforce}.

The FAIRE source manuscript additionally compares its intended force-history representation with FAWAM, which predicts future action and wrench trajectories, and identifies G-force as related work on robustness to contact-dynamics variation~\cite{he2026fawam,TODO_GForce}. These references delimit rather than establish FAIRE's novelty. FAIRE integrates temporal wrench encoding, desired-force prediction, and compliant execution specifically around polishing precision metrics.

\section{Motion--Force Demonstration Collection}
Contact-rich learning requires synchronized capture of task context, tool motion, and wrench. Kinesthetic teaching obtains demonstrations through the robot, whereas external devices can reduce dependence on a specific robot embodiment. ForceMimic is a direct precedent for a force--motion capture device used in contact-rich imitation~\cite{liu2025forcemimic}. Other surface-treatment interfaces emphasize intuitive task teaching and interactive programming~\cite{alt2024robogrind}.

FAIRE uses a handheld device instrumented with a six-axis force/torque sensor and tracked in a VR coordinate frame. Its method contribution is the calibrated transform chain that maps these measurements into the robot workspace while preserving synchronization with wrench and image streams. The use of six-axis sensing or external tracking alone is not presented as novel.

\section{Force, Impedance, and Admittance Control}
Compliant robot control regulates the relationship between motion and contact force. Impedance control specifies a desired dynamic relation between displacement and force, while admittance control maps measured force into a motion response~\cite{hogan1985impedance,villani2008forcecontrol,keemink2018admittance}. Admittance is particularly suitable when a learned policy supplies a force reference but the available robot interface accepts Cartesian motion commands.

In FAIRE, admittance control is the explicit bridge between prediction and physical execution. The force-tracking error drives a compliant position correction that is added to the imitated position reference. This formulation avoids describing the learned force as a direct actuator command and keeps safety filtering, saturation, and controller-rate implementation within the low-level execution layer.

\section{Residual Learning for Precision Correction}
Residual learning augments a nominal controller with a bounded learned correction. This decomposition is attractive for polishing because the demonstrated path and force trajectory already define task progress, while local changes in contact or curvature may require small adjustments. Related compliance-aware and reactive policies use learned fast corrections without assigning the learned residual responsibility for the complete task~\cite{hou2025adaptivecompliance,xue2025reactivediffusion}.

FAIRE applies this principle to two variables that directly affect surface processing. A velocity residual scales progress along the demonstrated stroke, and an orientation residual reduces the error between the tool normal and local surface normal. The intended novelty is their integration as polishing-specific precision layers above motion--force imitation and admittance execution, not residual RL as a general algorithm.

\section{Positioning of FAIRE}
\begin{table}[t]
\centering
\caption{Functional positioning of representative related approaches. Desired force denotes a policy-generated reference rather than force observation alone.}
\label{tab:related_work_comparison}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{lcccc}
\toprule
Method & Force observation & Desired force & Compliant execution & Polishing precision focus \\
\midrule
Vision-only IL~\cite{zhao2023act,chi2025diffusionpolicy} & No & No & No & No \\
AdmitDiff~\cite{zhou2024admitdiff} & Yes & Yes & Yes & No \\
ForceMimic~\cite{liu2025forcemimic} & Yes & Yes & Yes & No \\
FoAR~\cite{he2025foar} & Yes & No & Reactive & No \\
FAIRE & Yes & Yes & Yes & Yes \\
\bottomrule
\end{tabular}}
\end{table}

The research gap is therefore not the absence of force-aware learning. It is the need for a single precision-oriented polishing framework that connects calibrated human motion--force teaching, temporal force-conditioned imitation, controller-level force-trajectory execution, and bounded velocity and normal-alignment correction, and then evaluates each interface using continuous process metrics.
