\appendix
\chapter{Implementation and Experiment Checklists}
\section{Current Implementation Status}
\begin{itemize}
    \item Headlight ROI-mask interface: planned; ArUco ID must be converted to a spatial ROI mask outside the policy.
    \item Headlight full-coverage planning: planned; tool-footprint model, surface reconstruction, and registration must be verified.
    \item Aluminum geometry-based baseline: planned; perception, registration, IK, planning, and timing breakdown must be logged separately.
    \item Force-aware IL policy: architecture defined; exact observation/action channels must be verified from the final dataset and controller implementation.
    \item Low-level admittance controller: required shared execution layer; selected force/wrench channels and gains must be documented.
    \item RL velocity optimization and Preston-rate tuning: not a core contribution in the current thesis direction; keep only as optional future work unless separately validated.
\end{itemize}

\section{Recommended Dataset Fields}
Each demonstration episode should contain timestamps, local RGB or RGB-D images, ROI masks, robot joint state, end-effector pose, linear and angular velocity, measured six-axis force/torque, desired force reference if available, tool or spindle state, action chunk, phase labels, intervention labels, workpiece pose, target feature or ROI metadata, and success or failure annotations. Marker ID should be stored only as external command metadata and not used as a policy input.

\section{TODO Items Before Final Submission}
\begin{itemize}
    \item Verify whether the IL action is Cartesian pose, Cartesian increment, joint-space command, normal-force reference, three-axis force reference, or six-axis wrench reference.
    \item Fill in robot, sensor, controller, tool, fixture, and calibration details.
    \item Replace figure placeholders with final system, policy, headlight, aluminum, and timing figures.
    \item Set aluminum randomization ranges and trial counts after safety validation.
    \item Add quantitative headlight, aluminum, and force-ablation results only after experiments are completed.
    \item Report unresolved LaTeX warnings, overfull boxes, and citation issues before submission.
\end{itemize}

\section{Build Notes}
The project is compiled from \texttt{ThesisMain.tex}. A typical command is \texttt{latexmk -pdf ThesisMain.tex}. The cover can be compiled separately from \texttt{ThesisCover.tex}. The author, advisor, submission date, final figures, and experimental results are placeholders that must be updated before submission.
